Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.qmd
Commit

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 23

@@

```{r}
#| label: hexbin-regular-two-curvy3
## hexagon binning to have regular hexagons
hb_obj_two_curvy3 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 23, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 23, 
  r2 = r2
)$a1

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 15

@@

```{r}
#| label: hexbin-regular-two-curvy3
## hexagon binning to have regular hexagons
hb_obj_two_curvy3 <- hex_binning(
  data = tsne_two_curvy_scaled, 
  bin1 = 48, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 48, 
  r2 = r2
)$a1
